% !TEX program = lualatex
\PassOptionsToPackage{table}{xcolor}
%\PassOptionsToPackage{draft}{graphicx}
\documentclass{matthijs}
\graphicspath{{../assets/}{./docs/assets/}{./docs/advisory-report/}}

\begin{filecontents*}[overwrite]{\jobname.xmpdata}
	\Title{Internship Report}
	\Subject{Reflection on the project results}
	\Author{Matthijs Bakker}
	\Language{en-US}
	\Keywords{internship\sep final\sep written\sep report}
\end{filecontents*}

\input{preamble.tex}
\usepackage{titlepage}

\addbibresource{ir.bib}

% Typography
\babelfont{tt}{Inter-Regular}
\babelfont{rm}{Merriweather-LightItalic}
\usepackage{lettrine}

\definecolor{arobs blue}{HTML}{0e2642}
\definecolor{arobs comp}{HTML}{422a0e}
\definecolor{invisible}{rgb}{1,1,1}

% Page numbering
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\lfoot{\textcolor{invisible}{\gitAbbrevHash~\gitAuthorName~\gitAuthorIsoDate}}
\rfoot{\textbf{\thepage}\hspace{1ex}of\hspace{1ex}\pageref{LastPage}}

%\usepackage{tikz}
%\usepackage{tikz-uml}
%\usetikzlibrary{positioning, arrows.meta}

%\usepackage{tabularx}

\titleformat{\section}{\Large\bfseries\rmfamily\lsstyle\color{arobsblue}}{}{0em}{} [{\vspace{4pt}\titlerule[0.75pt]}]
\titleformat{\subsection}{\large\bfseries\rmfamily\lsstyle\color{arobsblue}}{}{0em}{} [{\vspace{4pt}\titlerule[0.75pt]}]

\renewcommand{\LettrineFontHook}{\rmfamily}

\begin{document}

	% Set language to English
	\taal{en}

	\maketitlepage{Internship Report}{1.0}
	\pagenumbering{arabic}
	\thispagestyle{empty}
	
	\lefthyphenmin=3
	\righthyphenmin=3

	\begin{hoofdstuk*}{Summary}

		\setlength\parindent{1.5em}
		\setlength{\parskip}{0.5em plus 0.2em minus 0.1em}
		\linespread{1.2}

		\lettrine[findent=0.3em, nindent=0.0em, lraise=0.03]{R}{esearch} conducted in the US by the National Highway Traffic Safety Administration in 2016 found that 94 percent of all motorvehicle accidents that year could be attributed to human error \cite{nhtsa2017fatal}.
		Twenty-one percent of these accidents were so-called ``run-off-road crashes.''
		This type of accident involves a single vehicle veering off the road and colliding with a natural or artifical object \cite{liu2009factors}.
		The most common causes were driver intoxication and fatigue \cite{nhtsa2017fatal}.

		The automotive department of AROBS is on a mission to enable vehicles to be more autonomous.
		By requiring less human input, cars can drive in a more predictable and safer manner.
		AROBS has been developing an Advanced Driver-Assistance System (ADAS) that consists of numerous subsystems which warn the driver of danger on the road.
		One of these subsystems is called the Lane Departure Warning System (LDWS).
		It predicts when the vehicle is about to leave the road lane and propagates a warning to the ADAS so that precautionary measures can be taken to prevent incidents.

		In order to detect the road lane that the vehicle is driving in, the LDWS analyzes video footage from a camera mounted on the dashboard.
		Resource-demanding image processing techniques are run on a Graphical Processing Unit (GPU) integrated in the vehicle's onboard computer to scan for road lane markings and to predict the position of the car.
		The GPUs used for this purpose are expensive and power-inefficient, raising the total cost of the system.

		Due to a global chip shortage since the start of the COVID-19 pandemic, the prices of semiconductors have spiked \cite{ivanova2021chip}.
		In particular, the prices of GPUs have surged up to 50 percent of their list price \cite{cheng2021chip}.
		This has led chip consumers like AROBS to explore alternative technologies.
		A popular alternative that can empower high-bandwidth image processing technologies are Field Programmable Gate Arrays.
		Whereas GPUs are multi-purpose devices which can programmed for many different tasks, FPGAs have to be specifically designed to do one single task.
		The FPGA designer has fine-grain control over the layout of the FPGA, enabling the possibility for creating devices that are tailored for a specific use case.
		An FPGA can be designed to do parallel tasks like video processing at a high bandwidth and low power draw, making is suitable for being integrated in embedded systems.

		The goal of my internship was to create a road lane marking detection system at a lower production cost and higher power efficiency than existing systems.
		I accomplished this goal by creating an FPGA-centered system that uses digital logic for its video processing task and a CPU for its decision making.
		The integration with other subsystems and devices is made possible through a UART interface.
		The device can process a video frame in 11.2 milliseconds and has an average power draw of 2.246 Watt.
		Compared to a popular GPU-oriented alternative, the Nvidia Jetson Nano, the system is four times more power efficient, 20 percent faster, and the production cost is seven times lower.
		A drawback of the system is that the lane marking detection does not work well under certain environmental conditions.
		The accuracy of detection depends on the quality of the road surface and lane markings, and the absence of roadside artifacts.
		The detection is too unreliable for a finalized product.

	\end{hoofdstuk*}

	\begin{inhoudspagina}

	\end{inhoudspagina}

	\pagenumbering{arabic}

	\begin{hoofdstuk*}{Preface}

	\end{hoofdstuk*}
	
	\begin{hoofdstuk}{Project Definition}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{The Product}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{Management and Control}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{Analyse}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{Advise}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{Design}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{Implementation}

	\end{hoofdstuk}
	
	\begin{hoofdstuk}{Professional Development}

	\end{hoofdstuk}

	% Bibliography page
	\begin{hoofdstuk}{References}

		\printbibliography[heading=none]

	\end{hoofdstuk}

	\makelastpage

\end{document}
